---
title: "Shiny Application and Reproducible Pitch"
output: ioslides_presentation
date: Apr 12, 2021
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction to Dataset
### Description: Growth of Orange Trees
The Orange data frame has 35 rows and 3 columns of records of the growth of orange trees.

### Variables
- **Tree**:
an ordered factor indicating the tree on which the measurement is made. The ordering is according to increasing maximum diameter.
- **age**:
a numeric vector giving the age of the tree (days since 1968/12/31)
- **circumference**: 
a numeric vector of trunk circumferences (mm). This is probably “circumference at breast height”, a standard measurement in forestry.

## An Overview of Dataset

```{r , echo = TRUE}
str(Orange)
```

## An Overall Scatter Plot

```{r ,echo = F}
library(ggplot2)
df <- Orange
df$Tree <- ifelse(
            df$Tree == 3, "A" , 
            ifelse(df$Tree == 1, "B" ,
                   ifelse(df$Tree == 5, "C",
                          ifelse(df$Tree == 2, "D", "E"))))
df$Tree <- as.factor(df$Tree)
ggplot(data = df, aes(circumference, age, color = Tree)) +
  geom_point() +
  coord_cartesian(xlim = c(0, 250), ylim = c(0, 2000))
```

## Boxplot

```{r ,echo=F}
library(ggplot2)
df <- Orange
df$Tree <- ifelse(
            df$Tree == 3, "A" , 
            ifelse(df$Tree == 1, "B" ,
                   ifelse(df$Tree == 5, "C",
                          ifelse(df$Tree == 2, "D", "E"))))
df$Tree <- as.factor(df$Tree)
ggplot(data = df, aes(circumference, age, fill = Tree)) +
  geom_boxplot() 
```
